brados: declarative, programmable object storage

### 2016-05-25 paper.tex

  # op's position was or was not found in the log
  scratch :found_op,    [:type, :pos, :epoch] => [:data]
  scratch :notfound_op, [:type, :pos, :epoch] => [:data]
end

bloom do
  # op's position found in log
  found_op <= (valid_op * log).lefts(pos => pos)
  notfound_op <= valid_op.notin(found_op)

  # demux on operation type
  write_op <= valid_op { |o| o if o.type == 'write' }
  read_op  <= valid_op { |o| o if o.type == 'read'  }
  fill_op  <= valid_op { |o| o if o.type == 'fill'  }
  trim_op  <= valid_op { |o| o if o.type == 'trim'  }
  seal_op  <= valid_op { |o| o if o.type == 'seal'  }
end
\end{lstlisting}

>>>>

  # op's position was or was not found in the log
  scratch :found_op,    [:type, :pos, :epoch] => [:data]
  scratch :notfound_op, [:type, :pos, :epoch] => [:data]
end
\end{lstlisting}

\begin{lstlisting}[caption={Setup}, label=lst:setup]
bloom do
  # op's position found in log
  found_op <= (valid_op * log).lefts(pos => pos)
  notfound_op <= valid_op.notin(found_op)

  # demux on operation type
  write_op <= valid_op {|o| o if o.type == 'write'}
  read_op  <= valid_op {|o| o if o.type == 'read'}
  fill_op  <= valid_op {|o| o if o.type == 'fill'}
  trim_op  <= valid_op {|o| o if o.type == 'trim'}
  seal_op  <= valid_op {|o| o if o.type == 'seal'}
end
\end{lstlisting}
